Systematic Design of Optimal Low-Thrust Transfers for the Three-Body Problem \thanks{This research has been supported in part by NSF under the grants CMMI-1243000 (transferred from 1029551), CMMI-1335008, and CNS-1337722.}

### 2018-05-23 Response.tex

            In short, the authors present a systematic method of generating optimal transfer orbits in the three-body problem.
            This paper provides a discrete optimal control formulation to generate the reachability set on a \Poincare section.
            % This results in an optimal solution rather than the suboptimal solution typical of direct optimal control methods which rely on coarse or suboptimal control parameterizations.
            % For example, a hybrid direct method may use a continuous control law developed from indirect optimal control theory while directly minimizing a cost function instead of solving the full two-point boundary value problem~\cite{ozimek2010a}.
            In addition, the use of a geometric integrators ensures numerical stability for long-duration orbit transfers and maintains this behavior with the addition of small magnitude control inputs.
            Our computation of the reachable set allows for a simple metric of defining optimal trajectories.
            We avoid the issues inherent in selecting a valid initial condition for optimization.
            Rather, we choose a state on the reachability set which minimizes the distance toward the desired target.
            We demonstrate these capabilities via two numerical examples simulating transfer trajectories in the Earth-Moon system.

        \end{correction}
\end{itemize}

\begin{itshape}
ISSUE 2: analysis/illustration (requires major revisions): 
My other highlighted area of concern with the original manuscript was the degree of (in)completeness in illustrating the method and its pros and cons.  I do not feel that the authors have done very much to improve this aspect of the paper beyond adding some caveats that feel a little half-hearted rather than properly contextualized discussions.  This aspect of the research remains a major shortcoming that must be addressed before publication.

While my request for improvements was itself not very specific, I had hoped that some of my other questions would reveal some areas of consideration for the authors.  Addressal/discussion of those questions furthermore needs to appear adequately in the paper, not just the rebuttal. Below I will try to sketch how these points of inquiry can lead to a more demonstrative analysis.
\end{itshape}
\newline\newline
Thank you for the comments and the additional suggestions to improve the manuscript. 
The main objective of the submitted manuscript is to construct a systematic approach to design low-thrust orbital maneuvers. 
It is motivated by the specific challenges that electric propulsion systems generate a minuscule level of thrust, and low-thrust orbital maneuvers rely on those effects accumulated over a long time period. 
Consequently, it is quite cumbersome and challenging to apply numerical optimization tools or boundary value problem solvers successfully to low-thrust orbital design problems. 
For example, it is difficult to initialize the optimization parameters such that the resulting numerical iteration converges successfully. 
Conventional numerical integration schemes have shown to be possibly erroneous particularly in computing long-term energy behaviors correctly.

In the submitted manuscript, we aim to provide more organized tools to mitigate such difficulties by explicitly considering the characteristics of the natural dynamics and utilizing geometric integrators exhibiting long-term numerical stability. 
The consideration of the natural, control-free dynamics is reasonable as low-thrust trajectories won't be drastically different from those over a limited time period. 
Here, the former is achieved by incorporating the control-free maneuvers characterized by the Poincare section in the invariant manifolds, and the latter is achieved by variational integrators.

However, the proposed scheme is focused on constructing low-thrust trajectories satisfying the prescribed boundary conditions, and it does not guarantee any optimality in the constructed maneuvers. 
It is heuristically implied that the constructed orbital maneuver would require no-excessive control input, as it is essentially constructed by adjusting the control-free trajectory. 
As such, it is rather focused on constructing a reasonable low-thrust trajectory that satisfies the given constraints on the maximum thrust bound and the boundary conditions.

In short,
\begin{itemize}
	\item[Pros] The proposed scheme utilizes the characteristics inherent in the three-body problem in constructing low-thrust orbital maneuvers in a systematic way. 
		This reduces the cumbersome process of guessing a \textit{good} set of initial parameters to make the direct application of optimization successful. 
	\item[Pros] The use of geometric integrators is particularly useful in capturing the long-term effects of low thrust in a computationally efficient manner. 
	\item[Cons] While the proposed scheme generates orbital trajectories to the target with prescribed constraints, it does not guarantee any optimality. 
\end{itemize}

In the revised manuscript, the conclusions section has been rewritten to summarize the above pros and cons of the proposed approach. 
\begin{correction}
In this paper, we construct a systematic approach which combines the concepts of reachability sets and \Poincare~sections to generate orbital transfers between planar periodic orbits in the three-body problem using low-thrust propulsion systems.
The \Poincare~section allows for trajectory design on a lower dimensional phase space thereby reducing the complexity and search space.
The approximation of the reachability set enables a simple methodology for the selection of \textit{good} initial parameters which will allow for convergence of the optimal control formulation.
The combination of these two concepts allows the engineer to capture the characteristics inherent in the three-body problem.
Additionally, we utilize geometric integrators to efficiently capture the long-term effects of low-thrust on the system dynamics.
Our approach enables the computation of orbital transfers within the three-body problem but does not guarantee optimality of the resulting transfer.
Instead, the resulting transfers will require no excessive control inputs as it is formulated as a deviation from the control-free trajectory.
The presented approach allows for a systematic method to determine and generate orbital transfers in the three-body problem using low-thrust propulsion.

@@

There is additional research to extend these results to more general transfer scenarios in future work.
The incorporation of fourth body perturbations, such as the Sun in the Earth-Moon system, offers an additional method of increasing the reachable set with the combined use of the solar perturbation and low-thrust propulsion.
In addition, the assumed acceleration magnitude is currently beyond the capabilities of current electric propulsion systems and future research is aimed at investigating smaller magnitude control inputs.
Furthermore, this analysis did not consider the effect of variable mass on the optimal control solution.
This will result in a more complicated optimal control problem and is a focus of future research.
Finally, Lyapunov control theory, which has previously been applied to the two-body problem, is being investigated in the hope of designing closed loop control schemes for this three-body scenario~\cite{chang2002}.
The addition of attitude dynamics and realistic pointing constraints would also significantly improve the applicability of this work.

\end{correction}

Also, the revised manuscript incorporates the suggested changes and additions.
We include several new figures to further illustrate the change in Jacobi energy.
In addition, we add some additional examples demonstrating the effect of variations in the control bound and terminal time on the reachability set.
These are itemized below.

@@

\begin{itemize}
    \item 
        \begin{itshape}
            The assumption of fixed travel time.  The authors respond that this choice is made to simplify the optimization problem.  Of course this is the case, and is conventional, but this choice is made in a rather arbitrary fashion rather than properly analyzed (especially considering that a central purpose of the problem setup is to enable faster travel times).  Imagine plotting low-thrust reachability curves as in Fig8b for each of a sequence of travel time choices.  This would reveal the influence of the arbitrarily handled parameter, and show that there's some critical point at which the reachablility curve intersects the targeted manifold.  Maybe exhaustive exploration of this dimension is not appropriate in every application, but the relationship is worth illustrating.
        \end{itshape}

        Thank you for the comment. 
        We agree that some further discussion of the effect of these ``tunable'' parameters would help to improve the manuscript. 
		According to the comments, we considered twelve additional cases for every combination of varying terminal time $t_f$ and the maximum control $u_m$ listed at Table \ref{fig:varying_tf_reachability_sets}. 
        An additional section has been included which highlights some of the effects of variations in terminal time, and control magnitude (next comment).
        The results presented are not an exhaustive description of the search space (in terms of travel time and/or control magnitude) but do highlight some of the important characteristics of these parameters on the resulting reachability set.
		According to the new numerical results, the manuscript has been revised to discuss the effects of varying $t_f$ and $u_m$ as copied below.

@@

            The reachable sets presented in~\cref{fig:varying_tf_reachability_sets} are highly dependent on the initial condition, terminal time, and maximum control bound. 
            This example demonstrates that increasing the \( u_m \) results in a larger displacement between the controlled and uncontrolled trajectories.
            The reachable set is enlarged from a single point, as shown in~\cref{fig:manifold_poincare} by the black point, to a larger region as shown in~\cref{fig:varying_tf_poincare}.
            The choice of \( u_m\), \( t_f \) and initial condition all combine to change the resulting reachability set.

        \end{correction}
    \item 
        \begin{itshape}
            The specification of a departure point from the periodic orbit.  In response to this question, the authors describe how the use of low-thrust propulsion enlarges the reachable set about some "center" defined by one branch of the uncontrolled manifold.  This is a key way to think about the approach you've posed but it is not illustrated in the paper.  Why not generate some curves under different thrust bounds for a specific departure point/manifold branch?  Again you'd be using a sidelined parameter to illustrate something fundamental about the approach.  And just maybe there would be a point at which, with high thrust, you start to see "bang-bang" type control and establish more connection to intuition.  
        \end{itshape}

        Thank you for the comment.
        We have included an additional section describing the effect of variations in \( u_m \) and terminal time on the reachable set.
        As discussed above, the results are not an exhaustive exploration of the parameter space but illustrate the key effect of the control bound and terminal time.
        In the example presented, increasing the magnitude of the control has the effect of enlarging and moving the reachable set. 
        At a sufficiently large value of \( u_m \) the reachable set is able to intersect the target orbit.

@@

    \item 
        \begin{itshape}
            Actually, the influence of the starting point selection *is* somewhat illustrated by the green unstable manifold of Fig7b/8b.  The way a mission designer might think about applying this tool could be to start with this information as a baseline and then use principles revealed by the preceding two types of illustration to make some informed way of selecting a combination of [departure point, travel time, max thrust] to get the sets to intersect without oversizing their system.  That said, it's a little confusing how the red and green curves of Fig8b don't line up with this description to fit the comment of P18L47; additional consideration/analysis may be needed with regards to the number of revs/crossings used to define a section for comparison.
        \end{itshape}

        Thank you for the comment.
        As stated in the previous comments we have included additional discussion on the effect of variations of terminal time and control bound.

        \begin{itshape}
That said, it's a little confusing how the red and green curves of Fig8b don't line up with this description to fit the comment of P18L47; additional consideration/analysis may be needed with regards to the number of revs/crossings used to define a section for comparison.
        \end{itshape}

        Thank you for the question. 
        The green points are the intersection of the unstable manifold with the \Poincare section while the red points are the reachability set.
        Without any control input the spacecraft would remain on the periodic orbit and intersect the \Poincare section at \( x_n\). 
        The addition of the control input allows for an expansion of the reachable set from a single point to the larger red region.
        An additional clarification has been added to the manuscript to aid in the description of the figure.

@@

    \subcaptionbox{Jacobi Energy: Energy history throughout the transfer.
    Each stage of the transfer serves to increase the energy towards the stable manifold. 
The final reachability set intersects the stable manifold and enables a large final manuever to the target orbit.\label{fig:jacobi_geo}}{\includegraphics[width=0.4\textwidth]{figures/geo_transfer/jacobi_energy.pdf}}

        \caption{Geostationary to \( L_1 \) periodic orbit transfer: Complete transfer from the geostationary orbit to the stable manifold.\label{fig:geo_transfer}}
\end{figure}
        \end{correction}
    \item 
        \begin{itshape}
            Following that thought, I have serious concerns about chaining this Poincare-based approach, as done in the second problem and as I previously asked about.  The authors' responded: "While the trajectories do return to the energy level of the Poincare section, there is a transfer of "energy" between the states of the vehicle." Frankly, this statement doesn't make sense to me.  I think that you are actually getting a very inefficient solution by forcing these repeated (and at fixed intervals) returns to the same energy level (again, plot the Jacobi time series and see if you can square it with your intuition).  Furthermore posing the problem as a transfer to the stable manifold kind of hamstrings the motivation of reducing transfer times.  Honestly, I think this second example should simply be axed.  If the first one is expanded enough to illustrate the problem fundamentals, it will be sufficient.  Conducting the same kind of analysis at a couple different rev counts would
            reveal the dimension that this second example added, and help reveal the limits of the approach under certain scenarios and thrust capabilities.
        \end{itshape}

		As pointed out by the reviewer, our prior response stating `..the trajectories do return to the energy level of the Poincare section..' is erroneous and misleading. 
        Instead, the combination of several reachability sets does not force the system to return to a prescribed energy level.
        Each reachability set computation serves to maximize a distance metric, defined in a reduced phase space corresponding to the \Poincare section.
        The cost function is computed as the distance between the terminal states of the controlled and uncontrolled trajectories.
        The additional plots shown in both examples highlight the fact that the Jacobi energy is continuously changing as the control input is used to maneuver the vehicle towards the desired target states.

@@

        The transfer to the stable manifold is presented as an example of the combination of existing control free  transfer methodologies with low thrust control inputs.
        This example demonstrates one possible use of low-thrust control to enable a larger region of feasibility for the use of invariant manifold transfers in the three body problem.

		With regards to the comments on the second example, the authors decided to keep them in the manuscript, as it illustrates the idea of multiple stages to construct orbital maneuvers with more challenging scenarios. 
		Nonetheless, the revised manuscript includes extended numerical results and discussions for the first example, for example to illustrate the effects of varying $t_f$ and $u_m$ and the evolution of the Jacobi constant. 
    \item 
        \begin{itshape}
            To summarize my thoughts on ISSUE 2:
            As they exist, the examples illustrate that solutions can be found but they do not enlighten the reader as to the characteristics of the problem formulation/tool that should be understood and kept in mind when applying it or when planning related research efforts.  Furthermore, I am very suspicious that Example 2 is not actually a good solution or a compelling use case for the approach.  I do not necessarily ask or expect the authors to follow my above outline precisely, but I insist that some changes occur to make the analysis/illustrations better convey the general nature of the tool, not just that it gives you an answer.  
        \end{itshape}

        Thank you for the comments.
        The manuscript has been edited, as described previously, to incorporate several changes to illustrate the specific characteristics of this approach.
        Also, an additional section is presented which highlights the effect of terminal time and control magnitude on the reachability set.

### 2018-05-23 manuscript.tex

The research in this work utilizes a variety of disparate concepts in dynamics, control theory, and astrodynamics. 
As a result, we briefly present some key concepts in the system model as well as established tools in the three body problem, such as invariant manifolds and \Poincare sections.
In addition, we summarize the derivation of a variational integrator for the PCRTBP which is used in the subsequent geometric optimal control formulation.
\subsection{Planar Circular Restricted Three Body Problem}\label{sec:pcrtbp}
The Earth is assumed to be the more massive primary, \( m_1 \), while the Moon is the second, smaller primary \( m_2\).
The equations of motion are developed in a rotating reference frame which allows for much greater insight into the structure of the dynamics.
Following convention, the system is also non-dimensionalized by the characteristic units of length, mass, and time~\cite{koon2011}.
As a result, the system can be characterized by a single mass ratio parameter \( \mu \),
\begin{equation}
        \mu = \frac{m_2}{m_1+m_2} \, .
        \label{eq:mass_param}
\end{equation}
In the rotating reference frame the Lagrangian is given by
\begin{equation}\label{eq:lagrangian}
    L = \frac{1}{2} \parenth{\parenth{\dot{x} - y}^2 + \parenth{\dot{y} + x}^2} + \frac{1 - \mu}{r_1} + \frac{\mu}{r_2},
\end{equation}
where the distances \( r_1, r_2 \in \R \) define the distance from the spacecraft to each primary and are defined as
\begin{align}
    r_1 &= \sqrt{\parenth{x + \mu}^2 + y^2} , \\
    r_2 &= \sqrt{\parenth{x -1 + \mu}^2 + y^2} .
\end{align}
Following a straightforward application of the Euler-Lagrange equations, a more detailed derivation is provided in~\cite{szebehely1967}, results in the following equations of motion defined in the rotating reference frame
\begin{equation}\label{eqn:cont_dyn}
        \left[\begin{array}{c} \dot{\vecbf{r}} \\ \dot{\vecbf{v}} \end{array} \right] = 
        \left[ \begin{array}{c} \vecbf{v} \\ A \vecbf{v} + \nabla U + \vecbf{u} \end{array} \right] = f\left( t,\vecbf{x}, \vecbf{u}\right) \, ,
\end{equation}
where the matrix \( A \) and psuedo gravitational potential gradient \( \nabla U\) are
\begin{align}
    A &= \left[ \begin{array}{ccc} 0 & 2 & 0 \\ -2 & 0 & 0 \\ 0 & 0 & 0 \end{array} \right], \label{eq:A_mat} \\
    \nabla U &= \left[ \begin{array}{c} x - \frac{ \left(1 - \mu\right) \left(x + \mu\right)}{r_1^3} - \frac{\mu \left( x - 1 + \mu \right)}{r_2^3} \\
                                                                                        y - \frac{ \left(1 - \mu\right) y}{r_1^3} - \frac{\mu y}{r_2^3} \\
                                                                                        - \frac{ \left(1 - \mu\right) z}{r_1^3} - \frac{\mu z}{r_2^3}\end{array}\right]
                                        = \left[\begin{array}{c} U_x \\ U_y \\ U_z\end{array} \right] , \label{eq:grav_pot}
\end{align}
and the control input is defined as \( \vecbf{u} = \begin{bmatrix} u_x & u_y \end{bmatrix}^T \in \R^{2\times1} \) and assumed to be continuously variable but bounded in magnitude, i.e. \( \vecbf{u}^T \vecbf{u} \leq u_{max}^2 \).
The state is defined as \( \vecbf{x} = \begin{bmatrix}\vecbf{r} &\vecbf{v} \end{bmatrix}^T\) with \(\vecbf{r} = \begin{bmatrix} x & y \end{bmatrix}^T \in \R^{2\times1}\) and \(\vecbf{v}= \begin{bmatrix} \dot{x} & \dot{y} \end{bmatrix}^T \in \R^{2\times1}\) representing the position and velocity with respect to the system barycenter, respectively.

@@

\subsubsection{Transfer to Periodic Orbit}~\label{sssec:periodic_orbit_transfer}
% reachable set transfer
Here we use the results of the preceeding section to demonstrate one specific example of a transfer designed using the reachability set.
The acceleration limit is chosen as  \( u_{max} = 0.75 \approx \SI{2}{\milli\meter\per\second\squared} \) in the Earth-Moon system.
Assuming a fixed spacecraft mass of \SI{500}{\kilo\gram}, this model defines a maximum thrust of approximately \SI{1}{\newton}.
Currently, the NASA NEXT xenon thruster is able to provide approximately \SI{0.25}{\newton} of thrust, and a cluster of such engines could be used to provide the desired thrust used in this work~\cite{schmidt2008}.
The trajectories are generated from a fixed initial state of \( \vecbf{x}_0 = \begin{bmatrix}0.8156 & 0 & 0 & 0.1922 \end{bmatrix}^T \) over a fixed time span of \( t_f = 1.4 \).
This initial state lies on the initial periodic orbit and the time of flight is equivalent to one half period of the initial periodic orbit.

@@

% generate the optimal transfer
\Cref{fig:poincare_compare} shows that the reachable set and those of the descending target region intersect.
As both regions are discretely approximated a linear interpolation is used to determine the exact intersection state on the \Poincare section.
This intersection generates a partial target state of \( x_t \text{ and } \dot{x}_t \).
Using the energy level of the target region, defined by~\cref{eq:jacobi}, and the intersection state we can calculate the final component \( \dot{y} \) is calculated. 
This results in a complete target state \( \vecbf{x}_t \) which lies on the reachable set and on the target orbit. 
A final optimal trajectory is generated such that the \( \vecbf{x}(N) = \vecbf{x}_t \).
This transfer trajectory is denoted by the green path in~\cref{fig:reach_transfer}.
The optimal control input is shown in~\cref{fig:control_l1}. 
The spacecraft achieves the desired target while satisfying the bounded control input.
The Jacobi energy integral, computed using~\cref{eq:jacobi}, is shown in~\cref{fig:jacobi_l1}.
\Cref{fig:jacobi_l1} shows that the vehicle begins with an energy level equal to the periodic orbit and arrives at the target orbit with the appropriate energy.
The first half of the transfer is associated with and increase in energy as the control is used to transition towards the target orbit which is followed by a energy decrease to the target orbit.
This roughly corresponds with the expected optimal solution of a bang-coast-bang type orbital transfer~\cite{kirk2012}.
Convergence statistics associated for this transfer are shown in~\cref{tab:l1_transfer_stats}.
\begin{table}
    \centering
    \begin{tabular}{llr}  
        \toprule
        Metric    & Value \\
        \midrule
        \texttt{fsolve} objective      & \num{6.03e-15}      \\
        \texttt{fsolve} major iterations       & \num{9}      \\
        \texttt{fsolve} first order optimality & \num{1.88e-13} \\
        Optimal cost       & \num{2.09e-31}      \\
        Executation time & \SI{1.49}{\second}       \\
        \bottomrule

@@

        Executation time & \SI{2.62}{\second}       \\

@@

    \subcaptionbox{Jacobi Energy: Energy history throughout the transfer.
    Each stage of the transfer serves to increase the energy towards the stable manifold. 
The final reachability set intersects the stable manifold and enables a large final manuever to the target orbit.\label{fig:jacobi_geo}}{\includegraphics[width=0.5\textwidth]{figures/geo_transfer/jacobi_energy.pdf}}

@@

\section{Conclusions}\label{sec:conclusion}
In this paper, we construct a systematic approach which combines the concepts of reachability sets and \Poincare~sections to generate orbital transfers between planar periodic orbits in the three-body problem using low-thrust propulsion systems.
The \Poincare~section allows for trajectory design on a lower dimensional phase space thereby reducing the complexity and search space.
The approximation of the reachability set enables a simple methodology for the selection of \textit{good} initial parameters which will allow for convergence of the optimal control formulation.
The combination of these two concepts allows the engineer to capture the characteristics inherent in the three-body problem.
Additionally, we utilize geometric integrators to efficiently capture the long-term effects of low-thrust on the system dynamics.
Our approach enables the computation of orbital transfers within the three-body problem but does not guarantee optimality of the resulting transfer.
Instead, the resulting transfers will require no excessive control inputs as it is formulated as a deviation from the control-free trajectory.
The presented approach allows for a systematic method to determine and generate orbital transfers in the three-body problem using low-thrust proplusion.

>>>>

The research in this work utilizes a variety of disparate concepts in dynamics, control theory, and astrodynamics. 
As a result, we briefly present some key concepts in the system model as well as established tools in the three body problem, such as invariant manifolds and \Poincare sections.
In addition, we summarize the derivation of a variational integrator for the PCRTBP which is used in the subsequent geometric optimal control formulation.
\subsection{Planar Circular Restricted Three Body Problem}\label{sec:pcrtbp}
The Earth is assumed to be the more massive primary, \( m_1 \), while the Moon is the second, smaller primary \( m_2\).
The equations of motion are developed in a rotating reference frame which allows for much greater insight into the structure of the dynamics.
Following convention, the system is also non-dimensionalized by the characteristic units of length, mass, and time~\cite{koon2011}.
As a result, the system can be characterized by a single mass ratio parameter \( \mu \),
\begin{equation}
        \mu = \frac{m_2}{m_1+m_2} \, .
        \label{eq:mass_param}
\end{equation}
In the rotating reference frame the Lagrangian is given by
\begin{equation}\label{eq:lagrangian}
    L = \frac{1}{2} \parenth{\parenth{\dot{x} - y}^2 + \parenth{\dot{y} + x}^2} + \frac{1 - \mu}{r_1} + \frac{\mu}{r_2},
\end{equation}
where the distances \( r_1, r_2 \in \R \) define the distance from the spacecraft to each primary and are defined as
\begin{align}
    r_1 &= \sqrt{\parenth{x + \mu}^2 + y^2} , \\
    r_2 &= \sqrt{\parenth{x -1 + \mu}^2 + y^2} .
\end{align}
Following a straightforward application of the Euler-Lagrange equations, a more detailed derivation is provided in~\cite{szebehely1967}, results in the following equations of motion defined in the rotating reference frame
\begin{equation}\label{eqn:cont_dyn}
        \left[\begin{array}{c} \dot{\vecbf{r}} \\ \dot{\vecbf{v}} \end{array} \right] = 
        \left[ \begin{array}{c} \vecbf{v} \\ A \vecbf{v} + \nabla U + \vecbf{u} \end{array} \right] = f\left( t,\vecbf{x}, \vecbf{u}\right) \, ,
\end{equation}
where the matrix \( A \) and pseudo gravitational potential gradient \( \nabla U\) are
\begin{align}
    A &= \left[ \begin{array}{ccc} 0 & 2 & 0 \\ -2 & 0 & 0 \\ 0 & 0 & 0 \end{array} \right], \label{eq:A_mat} \\
    \nabla U &= \left[ \begin{array}{c} x - \frac{ \left(1 - \mu\right) \left(x + \mu\right)}{r_1^3} - \frac{\mu \left( x - 1 + \mu \right)}{r_2^3} \\
                                                                                        y - \frac{ \left(1 - \mu\right) y}{r_1^3} - \frac{\mu y}{r_2^3} \\
                                                                                        - \frac{ \left(1 - \mu\right) z}{r_1^3} - \frac{\mu z}{r_2^3}\end{array}\right]
                                        = \left[\begin{array}{c} U_x \\ U_y \\ U_z\end{array} \right] , \label{eq:grav_pot}
\end{align}
and the control input is defined as \( \vecbf{u} = \begin{bmatrix} u_x & u_y \end{bmatrix}^T \in \R^{2\times1} \) and assumed to be continuously variable but bounded in magnitude, i.e. \( \vecbf{u}^T \vecbf{u} \leq u_{max}^2 \).
The state is defined as \( \vecbf{x} = \begin{bmatrix}\vecbf{r} &\vecbf{v} \end{bmatrix}^T\) with \(\vecbf{r} = \begin{bmatrix} x & y \end{bmatrix}^T \in \R^{2\times1}\) and \(\vecbf{v}= \begin{bmatrix} \dot{x} & \dot{y} \end{bmatrix}^T \in \R^{2\times1}\) representing the position and velocity with respect to the system barycenter, respectively.

@@

\subsubsection{Transfer to Periodic Orbit}~\label{sssec:periodic_orbit_transfer}
% reachable set transfer
Here we use the results of the preceding section to demonstrate one specific example of a transfer designed using the reachability set.
The acceleration limit is chosen as  \( u_{max} = 0.75 \approx \SI{2}{\milli\meter\per\second\squared} \) in the Earth-Moon system.
Assuming a fixed spacecraft mass of \SI{500}{\kilo\gram}, this model defines a maximum thrust of approximately \SI{1}{\newton}.
Currently, the NASA NEXT xenon thruster is able to provide approximately \SI{0.25}{\newton} of thrust, and a cluster of such engines could be used to provide the desired thrust used in this work~\cite{schmidt2008}.
The trajectories are generated from a fixed initial state of \( \vecbf{x}_0 = \begin{bmatrix}0.8156 & 0 & 0 & 0.1922 \end{bmatrix}^T \) over a fixed time span of \( t_f = 1.4 \).
This initial state lies on the initial periodic orbit and the time of flight is equivalent to one half period of the initial periodic orbit.

@@

% generate the optimal transfer
\Cref{fig:poincare_compare} shows that the reachable set and those of the descending target region intersect.
As both regions are discretely approximated a linear interpolation is used to determine the exact intersection state on the \Poincare section.
This intersection generates a partial target state of \( x_t \text{ and } \dot{x}_t \).
Using the energy level of the target region, defined by~\cref{eq:jacobi}, and the intersection state we can calculate the final component \( \dot{y} \) is calculated. 
This results in a complete target state \( \vecbf{x}_t \) which lies on the reachable set and on the target orbit. 
A final optimal trajectory is generated such that the \( \vecbf{x}(N) = \vecbf{x}_t \).
This transfer trajectory is denoted by the green path in~\cref{fig:reach_transfer}.
The optimal control input is shown in~\cref{fig:control_l1}. 
The spacecraft achieves the desired target while satisfying the bounded control input.
The Jacobi energy integral, computed using~\cref{eq:jacobi}, is shown in~\cref{fig:jacobi_l1}.
\Cref{fig:jacobi_l1} shows that the vehicle begins with an energy level equal to the periodic orbit and arrives at the target orbit with the appropriate energy.
The first half of the transfer is associated with and increase in energy as the control is used to transition towards the target orbit which is followed by a energy decrease to the target orbit.
This roughly corresponds with the expected optimal solution of a bang-coast-bang type orbital transfer~\cite{kirk2012}.
Convergence statistics associated for this transfer are shown in~\cref{tab:l1_transfer_stats}.
\begin{table}
    \centering
    \begin{tabular}{llr}  
        \toprule
        Metric    & Value \\
        \midrule
        \texttt{fsolve} objective      & \num{6.03e-15}      \\
        \texttt{fsolve} major iterations       & \num{9}      \\
        \texttt{fsolve} first order optimality & \num{1.88e-13} \\
        Optimal cost       & \num{2.09e-31}      \\
        Execution time & \SI{1.49}{\second}       \\
        \bottomrule

@@

        Execution time & \SI{2.62}{\second}       \\

@@

    \subcaptionbox{Jacobi Energy: Energy history throughout the transfer.
    Each stage of the transfer serves to increase the energy towards the stable manifold. 
The final reachability set intersects the stable manifold and enables a large final maneuver to the target orbit.\label{fig:jacobi_geo}}{\includegraphics[width=0.5\textwidth]{figures/geo_transfer/jacobi_energy.pdf}}

@@

\section{Conclusions}\label{sec:conclusion}
In this paper, we construct a systematic approach which combines the concepts of reachability sets and \Poincare~sections to generate orbital transfers between planar periodic orbits in the three-body problem using low-thrust propulsion systems.
The \Poincare~section allows for trajectory design on a lower dimensional phase space thereby reducing the complexity and search space.
The approximation of the reachability set enables a simple methodology for the selection of \textit{good} initial parameters which will allow for convergence of the optimal control formulation.
The combination of these two concepts allows the engineer to capture the characteristics inherent in the three-body problem.
Additionally, we utilize geometric integrators to efficiently capture the long-term effects of low-thrust on the system dynamics.
Our approach enables the computation of orbital transfers within the three-body problem but does not guarantee optimality of the resulting transfer.
Instead, the resulting transfers will require no excessive control inputs as it is formulated as a deviation from the control-free trajectory.
The presented approach allows for a systematic method to determine and generate orbital transfers in the three-body problem using low-thrust propulsion.
